\section{Introduction}

\subsection{Developer Recommendations}

% SE Decisions are important
Humans make approximately 35,000 decisions every day.\footnote{\url{https://go.roberts.edu/leadingedge/the-great-choices-of-strategic-leaders}} Likewise, software engineers are also frequently faced with choices to make while developing code. As our society becomes more dependent on software products~\cite{SoftwareEatWorld}, it is becoming increasingly important to find ways to improve the behavior and decision-making of software developers. In his book \textit{The New Kingmakers: How Developers Conquered the World}, Stephen O'Grady describes the influence of software engineers' choices on the economy and society by noting ``Developers are the most-important constituency in technology. They have the power to make or break business, whether by their preferences, their passions, or their own products...Developers are now the real decision makers in technology. Learning how to best negotiate with these New Kingmakers, therefore, could mean the difference between success and failure"~\cite[p.~3-4]{OGrady2013King}. Furthermore, the Hacker Noon blog refers to decision-making as ``the most undervalued skill in software engineering" and ``the most important skill in software development", even moreso than coding skills.\footnote{\url{https://hackernoon.com/decision-making-the-most-undervalued-skill-in-software-engineering-f9b8e5835ca6}} and Li and colleagues discovered that the ability to make effective decisions is an important characteristic of being a great software engineer~\cite{GreatSoftwareEngineer}. 

% Developers need help making decisions
While decision-making is an important aspect of software engineering, developers often make less than ideal choices in their work. For example, software engineers often avoid adopting useful \textit{developer behaviors}, or processes designed to support programmers in completing software development tasks. For instance, Johnson and colleagues found that developers rarely use static analysis tools to automatically check for defects and prevent errors in code~\cite{Johnson2013Why}. To help developers make better decisions, software engineering researchers have explored creating recommender systems to automatically guide users. The ACM International Conference on Recommender Systems (RecSys) defines recommender systems as ``software applications that aim to support users in their decision-making while interacting with large information spaces"~\footnote{\url{https://recsys.acm.org/}, as quoted by~\cite{RSSE}}. Fischer and colleagues also argue that \textit{active help systems} that can automatically make recommendations to users completing tasks are more effective than \textit{passive help systems} requiring users to seek help~\cite{Fischer1984ActiveHelpSystems}. Similarly, recommendation systems for software engineering are designed to actively assist developers in completing various tasks and provide information when making decisions in their work~\cite{RSSE}. For example, Spyglass is an automated recommender system for software engineers that suggests code navigation tools in the Eclipse integrated development environment (IDE) to help developers save time and effort while searching through code to complete programming tasks~\cite{Spyglass}. 

% Existing recommender systems not effective
While many automated suggestion approaches have been developed to help developers make better choices, research shows that face-to-face recommendations between humans are the most effective. Murphy-Hill and colleagues explored how developers discover new software engineering tools and found that \textit{peer interactions}, or the process of discovering tools from coworkers during normal work activities, are more effective compared to other technical approaches~\cite{Murphy-Hill2011PeerInteraction}. The main reason developers provided for peer interactions being the most effective mode of tool discovery is the respect and trust built between colleagues. However, even though face-to-face interactions are an effective method for developer recommendations, they are becoming less practical for recommendations in software engineering. For example, Murphy-Hill also discovered that peer interactions occur infrequently among developers in the workplace~\cite{Murphy-Hill2011PeerInteraction}. There are many barriers to peer interactions in industry, such as mandated tools and processes by management, \textit{physical isolation} where programmers are increasingly working alone remotely, and \textit{developer inertia} where software engineers do not feel the need to share or adopt new practices and tools~\cite{Murphy-Hill2015HowDoUsers}. Additionally, many automated systems have proven ineffective for improving developer decision-making. For example, Viriyakattiyaporn and colleagues found that the inability to deliver suggestions in a timely manner discouraged programmers from adopting recommendations to improve code navigation with Spyglass~\cite{viriyakattiyaporn2009challenges}. Thus, this points to a need for new paradigms for making effective recommendations to developers.

\subsection{Motivating Example}

To understand the impact of the decline of peer interactions and inadequacy of automated recommendation systems for software engineering on decision-making for software engineers, consider the example of Cassius. Cassius is an experienced software engineer maintaining several popular open source JavaScript projects on GitHub. However, he is unaware of several major bugs that exist in his repositories because he does not implement any static analysis tools in his projects. This is primarily because he is not familiar with useful tools to help developers automatically find and prevent defects in JavaScript code. Additionally, he is not compelled to use these tools because he has not had any exposure to them through his work and doesn't want to go through the hassle of integrating new systems into his workflow and development environment. Cassius normally works from home remotely, so he does not have many opportunities to learn about useful tools and processes during face-to-face interactions with peers. Various automated recommendations have also been ineffective in persuading Cassius to adopt new tools and practices. He often receives automated emails suggesting new tools, but usually ignores the these messages as marketing and spam. He also frequently observes pop-ups and tool tips recommending useful tools and features in his integrated development environment (IDE), but Cassius usually disregards those as well.

%Cassius also frequently visits online programming communities and blogs such as HackerNews\footnote{\url{https://news.ycombinator.com/}} and Dev.to\footnote{\url{https://dev.to/}}. However, even though he normally notices articles and posts about new tools while reading through developer blogs, this usually occurs while he is not working and outside of his development environment so he is not motivated and usually forgets to try integrating any of these new tools into his code.

One day, Cassius notices a new pull request on one of his repositories. The pull request introduces Cassius to ESLint\footnote{\url{https://eslint.org/}}, an open source static analysis tool for finding errors in JavaScript code. He notices the description provides valuable information such as what the tool does, how to use it, and an example bug reported within his project's code. After further inspection, he notices the PR also modified the build configuration files to automatically add the tool for it to run during the continuous integration builds for his project. He just needs to merge the pull requests to add the static analysis tool to his repositories. Furthermore, he notices the same pull request was opened by a bot on several of his other JavaScript repositories. Due to the feedback, location, and accessibility of the recommendation, Cassius decides to merge the pull requests and adopt static code analysis into his repositories. In this proposal, I will discuss research that investigates effective designs for automated recommendations to improve developer behavior.

\subsection{Research Overview}

My research goal is, given a developer who is unaware of a useful developer behavior in a development situation, identify the most effective strategy to convince them to adopt the behavior. This goal can also be summed up in the following research question posed by Greg Wilson, software engineering researcher and co-founder of Software Carpentry,\footnote{\url{https://software-carpentry.org/}} who tweeted: \\

\begin{blockquote}
``I think the most interesting topic for software engineering research in the next ten years is, \textit{`How do we get working programmers to actually adopt better practices?'}".\footnote{\url{https://twitter.com/gvwilson/status/1142245508464795649?s=20}}
\end{blockquote} \\

To encourage developers to adopt better practices, this work will analyze and evaluate developer behavior adoption through the lens of behavioral science and economics. Behavioral science research has examined how to encourage humans to make better decisions, embrace beneficial behaviors, and accept new ideas. One framework used to influence human behavior and decision-making is \textit{nudge theory}. A \textit{nudge} refers to any factor that impacts how people make a decision without providing incentives or banning alternatives~\cite{sunstein2008nudge}. Referring back to the motivating example, the automated pull request Cassius receives is an example of a nudge. Cassius is not rewarded for accepting the recommendation and merging the pull request into his project. He is not prohibited from using other static analysis tools besides ESLint or or just simply ignoring the suggestion and closing the PR. In this thesis, I will argue that implementing recommendations to software engineers as nudges can improve developer behavior. To study the impact of integrating nudge theory into developer recommendations, I will adhere to the following plan of work: 1) determine what makes recommendations effective to developers, 2) examine existing tools for recommending developer behaviors, and 3) create new automated systems and strategies to improve the effectiveness of recommendations to developers.

\subsection{Research Contributions}

The expected contributions of the research for this thesis include:

\begin{itemize}
    \item a \textit{conceptual framework} that uses nudge theory to characterize failures and propose improvements to developer recommendations,
    \item a set of \textit{experiments} to evaluate and provide evidence for the conceptual framework, and
    \item \TOOL, an \textit{automated recommender system} to nudge software engineers to adopt developer behaviors based on our framework.
\end{itemize}

