\section{Experiments and Evaluations}

This section describes completed, in progress, and planned studies for this thesis. The bracketed text represents short names for each experiment and the text in parentheses displays the status and semester of submission.


%Peer learning is the process of acquiring knowledge and skills through interactions with colleagues. This type of collaboration is also important for increasing learning among software engineers, however it rarely occurs in industry. For example, Murphy-Hill and colleagues found that interactions between developers is the most effective mode of tool discovery, but they also occur infrequently in practice~\cite{Murphy-Hill2011PeerInteraction}. There are many ways for open source software developers to convey information to peers, and this study aims to discover the best way to increase peer learning for GitHub users. This research seeks to gather data describing how developers react to learning about new tools through recommendations from varying systems: emails, project issues\footnote{https://help.github.com/en/articles/about-issues}, pull requests\footnote{https://help.github.com/en/articles/about-pull-requests}, and suggestions\footnote{https://github.blog/changelog/2018-10-16-suggested-changes/}. Then, we conduct an in-depth analysis on the preferred method reported by participants to determine how effective and useful that feature is for learning in practice.

\subsection{[\sugg] ``Title of Suggestions Paper" (In Submission, ICSE 2020)}

\subsubsection{Motivation:} Peer interaction is the process of acquiring knowledge and skills through in-person interactions with colleagues. This type of collaboration is also important for increasing learning among software engineers, however it rarely occurs in industry. Murphy-Hill and colleagues found that, while these interactions between colleagues are the most effective way software engineers discover new development tools, they also occur infrequently in the workplace~\cite{Murphy-Hill2011PeerInteraction}. One of the primary reasons peer interactions are declining is the \textit{physical isolation} barrier, where development teams are increasingly becoming distributing and working remotely~\cite{Murphy-Hill2015HowDoUsers}. GitHub recently introduced a new feature, \textit{suggested changes},\footnote{\url{https://help.github.com/articles/incorporating-feedback-in-your-pull-request/\#applying-a-suggested-change}} which fosters peer interactions online by allowing developers to recommend code changes to each other through this novel system. This research seeks to discover the impact of the recently introduced suggested changes feature by gathering data about the effectiveness of these suggestions, collecting feedback from developers about the new feature, and exploring how well the design of this feature generalizes to other types of recommendations. To our knowledge, this is the first study that analyzes the suggested changes feature. The results from this work provide implications to improve the effectiveness of automated recommendations to developers and are used to motivate the design of \TOOL.

\subsubsection{Suggested Changes:} GitHub released suggested changes as a public beta feature in October 2018. This recently introduced feature allows GitHub users to recommend code changes on pull requests to software developers. On a pull request, this feature allows reviewers to add a comment to a line of code and use the \suggtag tag to make a suggested change to the code. Then, the author of the pull request will see the suggested change on the line of code in question and can immediately commit, edit, or reject the proposed suggestion in the code. The feature has become extremely popular on GitHub, with developers ``quick to adopt suggested changes" into their workflow and over 100,000 reported uses within weeks of the initial release, accounting for approximately 4\% of pull request review comments and 10\% of code reviewers.\footnote{\label{SuggestBlog}\url{https://github.blog/2018-11-01-suggested-changes-update/}} We evaluated this feature because of its novelty and fit into our conceptual framework. To my knowledge, this is the first work to analyze the GitHub suggested changes feature.

\subsubsection{Research Questions:}

\begin{itemize}
    \item[\textbf{RQ1}] How effective is the suggested changes feature compared to other methods of recommendations on GitHub?
    \item[\textbf{RQ2}] What factors of the suggested changes feature make it useful for developers?
    \item[\textbf{RQ3}] How well does the suggested changes feature apply to other types of recommendations?
\end{itemize}

% \begin{table}[H]
%     \centering
%     \begin{tabular}{|p{4cm}|p{3cm}|p{5cm}|p{3cm}|} 
%     \hline
%         \textbf{Research Questions} & \textbf{Participants} & \textbf{Sampling and Instruments} & \textbf{Analysis} \\ \hline
%         How effective is the suggested changes feature compared to other methods of recommendations on GitHub (markdown comments, issues, and pull requests)? & Top forked repositories & Analyze pull request comments since October 2018 (introduction of suggestions). To find suggestions search for the \texttt{```suggestion...```} tag in comments. To determine if a suggestion was accepted then search for the line of code within the suggestion tag in the latest version of code for that file. Also will analyze applied markdown pull request comments (\texttt{```...```}), merged PRs, and closed issues during that time span. & Rate of acceptance for each (percentage) \\ \hline
%         What types of things do developers recommend with the suggested changes feature? & Top forked repositories & Analyze pull request comments since October 2018. To find suggestions search for the \texttt{```suggestion...```} tag in comments. To examine and categorize the types of changes, observe the types of files with comments making suggested changes (i.e. code files (.py, .java,...), configuration files (.xml, .yml,...), documentation (i.e. comment), etc.). Can also compare the same for md comments and pull requests files. Can examine labels for issues & Comparison of suggestion count and acceptance rate for code/config/docs/... \\ \hline
%         How do suggestions impact the speed of accepting recommendations from developers? & Top forked repositories & Analyze pull request comments from top forked repositories since October 2018. To find suggestions search for the \texttt{```suggestion...```} tag in comments. To determine time, observe difference between created\_at and merged\_at time for PRs with suggestions, PRs with md comments, PRs without suggestions or comments, and issues & average time \\ \hline \hline
%         What factors of the most useful method (GitHub suggestions) make it effective for recommendations to developers? or Why do developers find the most useful method (GitHub suggestions) useful? & humans & a) send survey to suggestees about their experience or b) in-person study asking participants to observe and comment on recommendations by email, suggestion, pull request, and issue... & Likert scale, Qualitative coding \\ \hline
        
%     \end{tabular}
%     \caption{Guzdial Chart}
%     \label{tab:my_label}
% \end{table}

\subsubsection{Methodology:} This research was a multimethodology study divided into three phases to gather and analyze data to answer each of our research questions. \\

\subsubsection{Phase 1:} \textit{Effectiveness}

\paragraph{Implementation.}

To gather data for analyzing \SUGGS, we wrote a Python script to automatically parse pull request comments for GitHub projects. On GitHub, pull requests are the primary way for developers to contribute to a project and review code changes before merging updates into the main code base~\cite{gousios2014pullrequests}. We found \SUGGS~on lines of code by searching for the ``\texttt{```suggestion...```}" markdown command  in pull request comments, and found other pieces of code in pull request comments that aren't suggestions by searching for the ``\texttt{```...```}" GitHub markdown tag. Since suggested changes are not supported by the GitHub API at the time of this work, we are confident in this approach to analyze \SUGGS because the suggested changes feature only supports proposing changes to one line of code at a time.

\paragraph{Projects.}

To examine the effectiveness of the suggested changes feature on GitHub, we mined the top-forked repositories. GitHub recommends making forks of projects to create pull requests and contribute to public repositories\footnote{\url{https://help.github.com/articles/fork-a-repo/}} and the suggested changes feature requires reviewer suggestions to be made on pull requests. The list of repositories used for this evaluation is available online.\footnote{link}

\paragraph{Study Design.} Compared suggested changes to pull requests and issues.

\paragraph{Data Analysis.}

We determined the effectiveness of \SUGGS by measuring \textit{acceptance} and \textit{timing}. Acceptance refers to the rate at which a suggestion proposed by reviewers was integrated in a subsequent commit. To determine acceptance, we checked if the recommended line of code existed in the final version of the pull request. After compiling a list of accepted pull request code suggestions, we also distributed a survey to GitHub users with publicly available email address on their profile who received a suggestion from a reviewer on their code. We asked 5-point Likert scale questions on the usefulness of the \SUGGS~tool and included open-ended free response questions for developers to provide information. We sought to find details about why users found this system effective for suggesting changes, accepting recommended changes, and performing code reviews. \\

\subsubsection{Phase 2:} \textit{Usefulness}

\paragraph{Participants.} Suggesters and suggestees.

\paragraph{Study Design.} The survey for this phase of the study was designed to collect quantitative and qualitative data. \\

\subsubsection{Phase 3:} \textit{Generalizability}

\paragraph{Participants.} We recruited professional software engineers to participate in the final phase of this study. These developers were recruited at local meetup events and personal connections. In total, \todo{n} software developers completed our user study in Phase 3 to examine how well the suggested changes feature generalizes to other types suggestions, such as development tool recommendations. The participants averaged 9.5 years of professional programming experience and all of them were familiar with the GitHub platform but none of them were familiar with the recently introduced suggested changes feature. Additionally, most of the participants had experience contributing to open source software and using development tools in some capacity.

\paragraph{Study Design.} tasks: different types of recommendations to view.

\subsubsection{Results:} Developers adopt suggestions because of the location of recommendations, actionability, etc...This results of this project have been submitted for publication at the 2019 Visual Languages and Human-Centric Computing (VL/HCC) conference.

\subsection{[\proc] ``Education Bot" (In Progress, Fall 2019)}

\subsubsection{Motivation:} Improve adoption and tool notifications for students on their final project.

\subsection{[\proc] ``Title of Process Approriate Recommendations Paper" (In Progress, Spring 2020)}

\subsubsection{Motivation:} Evaluation for \TOOL. Study will involve making these on a bunch of GitHub repos

\subsubsection{Research Questions:}

\begin{itemize}
    \item[\textbf{RQ1}] How do developers react to timely recommendations?
    \item[\textbf{RQ2}] How applicable are timely recommendations to projects?
\end{itemize}

\subsubsection{Methodology:}

\paragraph{Participants.}

Who are participants, how many, what experience do they have, etc.?

\paragraph{Tasks.}

Real-world software engineering tasks where tools would be useful.

\paragraph{Implementation.}

Dummy IDE plugin or git webhooks. Make timely and untimely recommendations to participants to see how they feel.

\paragraph{Data Analysis.}

Screen audio recordings. Gather whether tool was used or not, feedback, post-survey/interview,...

For RQ2, observed projects on GitHub to evaluate applicability.

\subsubsection{Results:} 

Time matters and software engineers find \timing are effective

\subsection{Automated Program Suggestion Recommendations (Proposed)}

\subsubsection{Motivation:} 

Our prior work suggests that spatial locality, temporal locality, and actionability are important for improving the effectiveness of automated recommendations. To evaluate an approach with high locality and actionability, we propose automatically generating \SUGGS as a method to recommend tools to developers. These suggestions will have high spatial and temporal locality, adding comments on the lines of code in recently opened pull requests. Additionally, they have high actionability with developers able to click a button to easily apply the suggestion to their code.

\subsubsection{Proposed Methodology:}

Find open pull requests that have errors reported by tools, automatically add a comment with a suggestion to fix the buggy line, observe whether suggestion is applied or ignored

\subsubsection{Hypothesis:}

We hypothesize that automated suggestions will increase the effectiveness of software engineering tool recommendations to developers. Our \sugg~study found that x\% of GitHub suggestions were accepted by developers...\todo{results from suggestions study}

\subsection{Automated Program Repair}

\subsubsection{Motivation:}

Automated program repair is a growing area of research in computer science and software engineering.\footnote{http://program-repair.org/} Another method for making recommendations to developers with actionability and locality is to automatically generate pull requests with fixes for issues found by software engineering tools.

\subsubsection{Proposed Methodology:}

Automatically create pull requests with fixes to errors found by software engineering tools. Analyze GitHub repos, find projects with bugs reported by a tool, automatically generate a pull request that fixes the bug and recommends the tool, observe if PRs are merged/closed/ignored... Pick a tool that provides fixes (i.e. some EP errors)

\subsubsection{Hypothesis:}

We hypothesize this approach to software engineering tool recommendations will be effective for developers. While the results from our \tele~study suggest that automated pull requests are ineffective, we believe this method for recommendations will be able to integrate better into developers' workflow. One of our participants mentioned a desire to know if bugs were worth fixing and another one asked ``Can you fix
the errors reported by your tool in the build?"~\cite{SorryToBotherYou}. Additionally, Weimer discovered that developers preferred bug reports and addressed issues faster with automatically generated patches~\cite{WeimerPatch}.
