\section{Research Plan}

This section presents the research plan for the completion of the work presented in this proposal for my dissertation. All studies are referred to by their short names given in Sections 3 and 6.

\subsection{Completed Projects}

I have completed and published the following projects for this research proposal:

\begin{itemize}
    \item[] \peer: VL/HCC 2017~\cite{VLHCC}
    \item[] \sorry: BotSE 2019~\cite{BotSE}
\end{itemize}

The preliminary research outlined in this proposal was also presented and published at the Doctoral Symposium for the International Conference on Software Engineering (ICSE 2019) in Montreal, Canada~\cite{Symposium}. Additionally, this work has been presented at various industry conferences including QECampX 2018~\cite{QECamp},\footnote{\url{https://www.qecamp.com/}, requires Red Hat employee login} a Red Hat quality engineering conference, and DevConf 2019~\cite{DevConf},\footnote{\url{https://devconf.info/us/2019}} an open source conference for software developers and technologists.

\subsection{Upcoming Projects}

The following projects are currently under submission or in progress for publication and plan to complete in Spring 2020:

\begin{itemize}
    \item[] \sugg: ICSE 2020*
    \item[] Dissertation: Summer/Fall 2020*
    \item[] \nudge: ICSE SEET 2021*
\end{itemize}

The GitHub suggested changes study is currently under submission to ICSE 2020. We plan to complete the evaluation for \TOOL next semester and submit our results to the Software Engineering Education and Training track at ICSE 2021. Additionally, I plan to complete the majority of the drafting for my dissertation in Spring 2020.

\subsection{Proposed Timeline}

Table~\ref{tab:timeline} presents a detailed timeline outlining the completion of the remaining research proposed in this document. This plan does not include completed projects and preliminary work.

\begin{table}[H]
\centering
\caption{Research Timeline}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c|c|c|c|c| } \hline
  & \textbf{Sept} & \textbf{Oct} & \textbf{Nov} & \textbf{Dec} & \textbf{Jan} & \textbf{Feb} & \textbf{Mar} & \textbf{Apr} & \textbf{May} & \textbf{June} & \textbf{July} & \textbf{Aug} & \textbf{Sept} & \textbf{Oct} \\ \hline
  \multicolumn{15}{|c|}{\sugg} \\ \hline
  Data Analysis & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & & & & & & & & & & \\ \hline
  Rebuttal & & & \cellcolor{black} & & & & & & & & & & & \\ \hline
  \multicolumn{15}{|c|}{\nudge} \\ \hline
  Development & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & & & & & & & & \\ \hline
  Pilot & & & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & & & &  & & & &\\ \hline
  Data Collection & & & & & & & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & & & & &\\ \hline
  Data Analysis & & & & & & & & \cellcolor{black} & \cellcolor{black} & & & & &  \\ \hline
  Writing & & & & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & 
  \cellcolor{black}\\ \hline
  Submission & & & & & & & & &  & & & & & \cellcolor{black} \\ \hline
  \multicolumn{15}{|c|}{\diss} \\ \hline
  Writing & & & & & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \cellcolor{black}
  & \cellcolor{black} & \cellcolor{black} & \cellcolor{black} & \\ \hline
  Defense & & & & & & & & & \cellcolor{black} & \cellcolor{black} & 
  \cellcolor{black} & \cellcolor{black} & \cellcolor{black}
  & \\ \hline

\end{tabular}
\label{tab:timeline}
\end{table}

* These milestones depend on acceptance and publication into top software engineering conferences. In case of paper rejection or other schedule delays, additional submission venues include ASE, MSR, VL/HCC, CSCW, RecSys, TSE, and TOSEM, along with other peer-reviewed software engineering conferences and journals.

\section{Thesis Contract}

My dissertation will consist of the following deliverables for the committee upon the completion of this research:

\begin{todolist}
  \item Dissertation chapter on the \peer study.
  \item Dissertation chapter on the \sorry study.
  \item Dissertation chapter on the \sugg study.
  \item Dissertation chapter on the \proc study.
\end{todolist}
